---
title: "Final Project"
author: "Boxuan Li, Yangwei Yan, Yunqiu Yao, Lu Gan"
date: "12/5/2017"
output: 
  html_document:
    code_folding: hide
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = F,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(janitor)
library(ggthemes)
library(ggridges)
library(stringr)
library(forcats)
library(tidytext)
library(viridis)
library(anytime)

theme_set(theme_bw())
theme_update(legend.position = "bottom")
```

## Read and Clean the Dataset
```{r Read and clean}
ted <- read_csv("./data/TED.csv") %>%
  clean_names() %>%
  mutate(no = row_number()) %>% 
  select(no, everything(),-event, -film_date, -num_speaker, -related_talks, -name)
```

# Part 1 TED Topics

```{r}
## Tidy the "published_date" variable. 
## Convert UNIX timestamps into regular date form.
ted = ted %>%
  mutate(published_date = anydate(published_date)) %>%
  separate(published_date, into = c("year", "month", "day"), sep = "-")
## Tidy the "tags" variable.
ted_topic = ted %>%
  select(no, tags, views, year, month, day) %>%
  unnest_tokens(word, tags) %>%
  rename(topic = word)
```

We are interested in the topics TED talked most. The table and figure below show the top 10 topics with the most talks.
```{r}
## How many videos for each topic
n_topic = ted_topic %>% 
  group_by(topic) %>%
  count() %>%
  arrange(desc(n)) %>%
  ungroup

## filter top 10 topics with the most videos 
top10_topic = head(n_topic, 10)
knitr::kable(top10_topic, align = "c")
## Visualize the result
top10_topic %>%
  mutate(topic = fct_reorder(topic, n)) %>%
  ggplot(aes(x = topic, y = n, fill = topic)) +
    geom_bar(stat = "identity") +
    labs(
      x = "TED Topic",
      y = "Number of talks"
    )
```

TED includes talks on `r count(distinct(n_topic))` different topics. The figure above demonstrates the most 10 talked topics. Obviously, *Technology* is the topic with the most `r n_topic[1,2]` talks.

Also, we would like to explore the popuarity of topics. The figure below shows the the distribution of views for top 10 topics.
```{r}
## Visualize the distribution of views for top 10 topics.
ted_topic %>%
  filter(ted_topic$topic %in% top10_topic$topic) %>%
  mutate(topic = fct_reorder(topic, views)) %>%
  ggplot(aes(x = topic, y = views, fill = topic)) +
    geom_violin() +
    ylim(0, 5e+6) +
    stat_summary(fun.y = median, geom = "point", size = 2) +
    labs(
      x = "Topic",
      y = "Number of views for each video"
    )
```

We find that all the distributions of views are heavily right skewed, which indicates that some of the videos are extremely popular. 
We reordered the distributions by the median of views. Among the most talked 10 topics, culture and business had the highest median number of views. Therefore, what interests people most are talks related to culture and business.

To further explore how TED talks change over time, we plot two related figures below.

```{r}
## Visualize the number of TED topics through the years.
ted_topic %>%
  filter(ted_topic$topic %in% top10_topic$topic) %>%
  group_by(year, topic)%>%
  count() %>%
  ggplot(aes(x = year, y = n, group = topic, color = topic)) +
    geom_line() +
    labs(
      x = "Year",
      y = "Number of topics")

## Visualize TED topics views through the years.
ted_topic %>%
  filter(ted_topic$topic %in% top10_topic$topic) %>%
  ggplot(aes(x = year, y = views, fill = topic)) +
    geom_bar(stat = "identity", position = "fill") +
    labs(
      x = "Year",
      y = "Fraction")
```

The first figure above shows how many videos talking about top ten topics in each year. It seems that the topic "TEDx" are frequently used in 2012. TEDx was created in the spirit of TED's mission, "ideas worth spreading." It supports independent organizers who want to create a TED-like event in their own community. In March 2012, TED-Ed was launched, creating short video lessons aimed at educators, and April 2012 saw the debut of TED Radio Hour, a partnership that brings ideas and stories from TED Talks to public radio listeners. All of these projects may result in the increase of TEDx.
In 2016, we also see a peak in the increase of topic talking frequency. There are several global events held in 2016, including "TED 2016 Dream", which is a week-long conference about ideas, happening February 15-19, 2016, in Vancouver, BC, Canada.

The second figure above shows the fraction of views for top 10 topics through the years. We can see that culture have been viewed most in 2006 when the first six TED Talks were posted online. The topic "changes" drew more and more attention along the years.


# Part 3 Sentiment Analysis
(1) Tidy the *ratings* variable
```{r}
ratings = ted %>%
  select(no, ratings) %>% 
  mutate(ratings = substring(ratings,3, nchar(ratings)-2)) %>% 
  mutate(ratings = str_split(ratings,"\\}, \\{")) %>% 
  unnest(ratings) %>% 
  mutate(rat.words = sub(".*name': '(.*?)',.*", "\\1", ratings),
         rat.words = tolower(rat.words),
         rat.cnt = as.numeric(sub(".*'count': ", "", ratings))) %>%
  select(-ratings) %>% print()
```

(2) Perform sentiment analysis
```{r}
### read the sentiment dataset from 'bing'
bing_sent = get_sentiments("bing")

#### calculate sentiment value for each observation
rat_sent = ratings %>% 
  rename(word = rat.words) %>% 
  inner_join(bing_sent, by="word") %>% 
  group_by(no,sentiment) %>% 
  summarize(sum_cnt = sum(rat.cnt)) %>% 
  ungroup() %>% 
  spread(sentiment, sum_cnt) %>% 
  mutate(sentiment = (-1) * negative + positive) %>% 
  select(-negative, -positive) %>% 
  left_join(ted) 

### perfrom sentiment analysis
rat_sent %>% 
  mutate(no = factor(no),
         no = fct_reorder(no, sentiment)) %>% 
  ggplot(aes(no, sentiment, fill=views, color=views)) +
    geom_bar(stat = "identity") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) + 
    scale_fill_viridis() +
    scale_color_viridis()

### try the cube root to reduce skewness
rat_sent %>% 
  mutate(no = factor(no),
         no = fct_reorder(no, sentiment),
         cubert = ifelse(sentiment > 0, sentiment^(1/3), -(-sentiment)^(1/3))) %>% 
  ggplot(aes(no, cubert, fill=views, color=views)) +
    geom_bar(stat = "identity") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) + 
    ylab("cube root of sentiment") +
    scale_fill_viridis() +
    scale_color_viridis()
```

Here in the sentiment analysis, first we extract the sentiment words and the corresponding counts that are nested in the variable *ratings* for each observation, and assign them to two new variables *rat.words* and *rat.cnt*. Then we match the rating words (*rat.words*) with the sentiments dataset from 'bing', defining the rat.words as 'positive' or 'negative'. For each inspection number(*no*), we calculate the difference of sum of positive count and sum of negative count and use it as the sentiment score for this observation. 

After obtaining the sentiment score, we start to make a plot showing the inspection sentiments and the number of viewers. We first coerce the *no* variable to factor and reorder it accorrding to the sentiment score and plot the realtionship between inspection number and sentiment score. However, since there are some observations with extremely large score, making the graph rather skewed, we try the cube root of the outcome (*sentiment*) and plot again to obtain the second graph. It can be seen that most of the ted talks have positive sentiment ratings, since only a small portion on the plot is in the negative side of y axis. Further, we find out that those ted talks with large number of viewers also receive high ratings, since the color yellow and green, which indicate a higher viewers, mostly appear at the right side of the plot, where the sentiment scores are high.

(3) Compare top 10 talks picked by viewers and ratings respectively
```{r}
top10_sent = rat_sent %>% 
  arrange(desc(sentiment)) %>% 
  head(10) %>% print()

top10_view = ted %>%
  arrange(desc(views)) %>% 
  head(10) %>% print()

```

### Tidy the *speaker_occupation* variable
```{r, warning = FALSE}
speaker = ted %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove"), sep = "/") %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove1"), sep = ",") %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove2"), sep = ";") %>% 
  select(-remove, -remove1, -remove2) %>% 
  mutate(speaker_occupation = str_to_lower(speaker_occupation)) %>% 
  mutate(speaker_occupation = str_replace(speaker_occupation, "author", "writer"))

```
We know from the dataset that in speaker_occupation variable, one speaker might have more than one occupation. We also find that the first occupation is the main occupation of the speaker which can best represents their main focus, so we clean the speaker_occupation variablt to leave only the first occupation in the data set. Also, we discover that there exists writer and author in this variable and they represent the same occupation, so we replace the author with writer.

### Find out the top ten speaker occupation
```{r}
speaker %>% 
  group_by(speaker_occupation) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  pander::pander()
```

From the above table, we find out that the most popular speaker occupation is writer, and totally 107 writers came and gave TED Talks. Then comes to artist and designer, journalist, entrepreneur, inventor, architect, psychologist, neuroscientist and physicist. We are surprised to find out that the top four occupations are all about arts, indicating that people who work with arts are more willing to give a TED Talk and their talks might attract more viewers.


