---
title: "Why is a TED Talk Popular?"
author: "Lu Gan, Yangwei Yan, Yunqiu Yao, Boxuan Li"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(janitor)
library(ggthemes)
library(ggridges)
library(stringr)
library(forcats)
library(tidytext)
library(viridis)
library(anytime)
library(wordcloud)
library(plotly)

theme_set(theme_bw())
theme_update(legend.position = "bottom")
```


```{r Read and clean, message=FALSE, warning=FALSE, include = FALSE}
## Read and basically clean the dataset
ted.data <- read_csv("./data/TED.csv")

head(ted.data,10)

## Add the column of no.
ted <- read_csv("./data/TED.csv") %>%
  clean_names() %>%
  mutate(no = row_number()) %>% 
  select(no, everything(), -event, -film_date, -related_talks, -name)

## Tidy the "published_date" variable. 
## Convert UNIX timestamps into regular date form.
ted = ted %>%
  mutate(published_date = anydate(published_date)) %>%
  separate(published_date, into = c("year", "month", "day"), sep = "-")
```

## Introduction

### Background
TED (Technology, Entertainment, Design) is an organization that posts talks online for free dissemination. TED was founded in 1984 as a conference and has developed a lot so far. And nowadays, it has become the symbol of idea gathering, rooted into our life everywhere around. These talks, full of wisdom, have been increasingly drawing attention from public, and are playing imporatant roles in spreading ideas.

### Motivation
Members in our group have always been fascinated by TED talks and the marvelous diversity of the contents (shown in the fantastic topic cloud below). An idea therefore came to our mind that we can try to explore what exactly affects the popularity of a TED talk by combining the skills out of the data science courses and some strategies to operate the data obtained. 

```{r warning=FALSE, message=FALSE}
## Create a word cloud for ted topics.
## Tidy the "tags" variable.
ted_topic = ted %>%
  select(no, views, year, month, day, tags) %>%
  mutate(tags = substr(tags,3,nchar(tags)-2),
         tags = str_split(tags, "', '")) %>% 
  unnest(tags) %>% 
  rename(topic = tags)

## The frequence of appearance for each topic
n_topic = ted_topic %>% 
  group_by(topic) %>%
  count() %>%
  arrange(desc(n)) %>%
  ungroup

## Create the word cloud
set.seed(1234)
wordcloud(words = n_topic$topic, 
          freq = n_topic$n, 
          min.freq = 1,
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.35, 
          colors = brewer.pal(8, "Dark2"))
```

### Data
In this study, the collected dataset that covers the overall information about `r dim(ted.data)[1]` TED talks from June 26th, 2006 to September 21st, 2017, is hosted on the official TED.com website. The detailed information about the original dataset can be referred to the "Dataset" page on the navigation bar.

### Objectives

In this study, we try to explore the connection of the popularity of a TED talk with other varibales and answer a few questions that may explain what makes a TED talk popular:

1. What are the most popular TED topics? How did the popular topics change over time?       
2. Who are the most popular TED speakers? What are the occupations of popular TED speakers? Do some professions tend to attract a larger number of viewers?
3. How the ratings of viewers look like? How many positive and negative words in the ratings?
4. Is that possible to build a model to illustrate the relationship between the popularity of a TED talk and other varibales?


## Methods

In this study, we follow a step-by-step analysis to reveal the association between the popularity and other variables with the popularity of one TED talk represented by the number of views (variable "views").

1) The __topic__ of each TED talk is extracted primarily from the "tag" variable for each TED talk by means of operation of strings, which can be summarized subsequently. As a result, the most frequently appeared topics are ranked out assissted with tables and plots.

2) With similar strategies, the connection of popularity of a TED talk with its __speaker__ can be figured out. In this part, we realized that some frequently appeared terms of occupation almost have the same meaning, e.g. "author" and "writer". Therefore, we decided to unify them with one term. And speakers with multiple occupations will be treated with their first occupation. Finally, a boxplot is made to present the distribution of views for speaker_occupation.

3) In this study, the variable "ratings" is splitted to extract particular reviews for each TED talk. Then __sentiment__ of that talk will be calculated based on the positiveness of each review after combininig with "bing" and the counts. Furthermore, sentiment analysis can be conducted based on the barplot.

4) After foregoing anaylysis, we would like to take other covariates that are not invovled into consideration. Hence, we will further explore the __linear realtionship__ between the number of views for each talk and other predictors. In this case, "year" is categorized into three arms, "before 2010" (2006-2009), "between 2010 and 2015" (2010-2014) and "after 2015" (2015-2017) and the first arm will serve as reference level.

## Results and Analysis

### 1) Topic vs. Popularity

```{r}
## filter top 10 topics with the most talks 
top10_topic = head(n_topic, 10)
## Visualize the result
gg_top10 = top10_topic %>%
  mutate(topic = fct_reorder(topic, n)) %>%
  ggplot(aes(x = topic, y = n, fill = topic)) +
    geom_bar(stat = "identity")

ggplotly(gg_top10) %>% 
  layout(xaxis=list(title = "TED Topic"),
         yaxis=list(title = "Number of talks"),
         title="Top10 most talked topics")
```

TED includes talks on `r count(distinct(n_topic))` different topics. The figure above demonstrates the most 10 talked topics. Obviously, *Technology* is the most talked topic with `r n_topic[1,2]` talks.

```{r}
## Visualize the number of TED topics through the years.
gg_talks_years = ted_topic %>%
  filter(ted_topic$topic %in% top10_topic$topic) %>%
  group_by(year, topic)%>%
  count() %>%
  ggplot(aes(x = year, y = n, group = topic, color = topic)) +
    geom_line() 

ggplotly(gg_talks_years) %>% 
  layout(xaxis=list(title = "Year"), 
         yaxis=list(title = "Number of talks"),
         title = "Talks of top10 topics across years")
```

The figure above shows how many videos talking about top 10 topics in each year. The topic "TEDx" are frequently mentioned in 2012. TEDx is a program supporting independent organizers who want to create a TED-like event in their own community. In 2012, a week-long event-TEDx Summit was held by the Doha Film Institute, the inaugural event gathered TEDx organizers from around the world for workshops, talks and cultural activities. It may result in the increase of TEDx talks in 2012. 2016 also witnesses a peak in the increase of all the talks. There are several global events held in 2016, including "TED 2016 Dream" in Canada, which is a conference about ideas.


### 2) Speaker vs. Popularity
```{r, warning = FALSE}
speaker = ted %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove"), sep = "/") %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove1"), sep = ",") %>% 
  separate(speaker_occupation, into = c("speaker_occupation", "remove2"), sep = ";") %>% 
  select(-remove, -remove1, -remove2) %>% 
  mutate(speaker_occupation = str_to_lower(speaker_occupation)) %>% 
  mutate(speaker_occupation = str_replace(speaker_occupation, "author", "writer"))

```
 
```{r}
speaker %>% 
  group_by(main_speaker) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ungroup()%>% 
  mutate(main_speaker = fct_reorder(main_speaker, n)) %>%
  ggplot(aes(x = main_speaker, y = n)) +
  geom_col(aes(fill = main_speaker)) +
  coord_flip() +
  labs(
    title = "visualization of the ten top speakers",
    x = "main speaker",
    y = "number of talks")
```

From the above table, we find out that statistician Hans Rosling gave most TED Talks among all the TED speakers. As a professor of global health at Sweden's Karolinska Institute, his current work focuses on dispelling common myths about the so-called developing world. The range of the number of TED Talks given by top ten speaker is from 5 to 9, probably indicates that these speakers are very popular among viewers and they give TED Talks frequently.

```{r}
speaker %>% 
  group_by(speaker_occupation) %>% 
  summarize(number_talks = n()) %>% 
  arrange(desc(number_talks)) %>% 
  head(10) %>% 
  pander::pander()
```

Based on the results in the table above, most speakers attending the TED talks are writers. Then comes to artist and designer, journalist, entrepreneur, inventor, architect, psychologist, neuroscientist and physicist. We are surprised to find out that the top four occupations are all about arts, indicating that people who work with arts are more willing to give a TED Talk and their talks might attract more viewers.

```{r, message=FALSE, warning=FALSE}
gg_views_occ = speaker %>% 
  filter(speaker_occupation %in% c("writer", "artist", "designer", "journalist", "entrepreneur", "inventor", "architect", "psychologist", "neuroscientist", "physicist")) %>% 
  mutate(speaker_occupation = fct_reorder(speaker_occupation, views)) %>% 
  ggplot(aes(x = speaker_occupation, y = views)) +
  geom_boxplot(aes(fill = speaker_occupation), alpha = .9) +
  ylim(0,7.5e+06)

ggplotly(gg_views_occ) %>% 
  layout(title="Views for talks from top10 speaker occupations",
         yaxis=list(title="Views"),
         xaxis=list(title="Speaker occupation"))
```

From the resulted boxplot, we find that psychologist has the highest median, indicating that TED Talks given by psychologist are more popular and attract more viewers than TED Talks given by speakers with other occupations. In addtion, it can be discovered that there are always some extreme points for each occupation. It is easy to be understood because these talks may be given by the most famous or authoritative people in that field or the content of that talk is relevant to the hottest foucs at that time. 

### 3) Sentiment analysis

Here in the sentiment analysis, we extract the sentiment words and the corresponding counts for each observation, and define the words as 'positive' or 'negative' accroding to [Bing sentiment analysis](https://www.cs.uic.edu/~liub/FBS/sentiment-analysis.html). Then we calculate sentiment score for each observation as difference of the sum of positive and negative counts. The visualization of the distribution of sentiment follows with a plot, showing the distribution of sentiment score. Since the plot with original sentiment score on y-axis are highly skewed, we transform the score to its cube root to help visualize.

```{r}
ratings = ted %>%
  select(no, ratings) %>% 
  mutate(ratings = substring(ratings,3, nchar(ratings)-2)) %>% 
  mutate(ratings = str_split(ratings,"\\}, \\{")) %>% 
  unnest(ratings) %>% 
  mutate(rat.words = sub(".*name': '(.*?)',.*", "\\1", ratings),
         rat.words = tolower(rat.words),
         rat.cnt = as.numeric(sub(".*'count': ", "", ratings))) %>%
  select(-ratings)
```

```{r, message=FALSE}
### read the sentiment dataset from 'bing'
bing_sent = get_sentiments("bing")

#### calculate sentiment value for each observation
rat_sent = ratings %>% 
  rename(word = rat.words) %>% 
  inner_join(bing_sent, by="word") %>% 
  group_by(no,sentiment) %>% 
  summarize(sum_cnt = sum(rat.cnt)) %>% 
  ungroup() %>% 
  spread(sentiment, sum_cnt) %>% 
  mutate(sentiment = (-1) * negative + positive) %>% 
  select(-negative, -positive) %>% 
  left_join(ted) 

### try the cube root to reduce skewness
gg_trans_sent = rat_sent %>% 
  mutate(no = factor(no),
         no = fct_reorder(no, sentiment),
         cubert = ifelse(sentiment > 0, sentiment^(1/3), -(-sentiment)^(1/3))) %>% 
  ggplot(aes(no, cubert, fill=views, color=views)) +
    geom_bar(stat = "identity") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) + 
    scale_fill_viridis() +
    scale_color_viridis()

ggplotly(gg_trans_sent) %>% 
  layout(yaxis=list(title="Cube root of sentiment"))
```

It can be seen that most of the ted talks have positive sentiment ratings, since only a small portion on the plot is in the negative side of y axis. Further, we find out that those ted talks with large number of viewers also receive high ratings, since the color yellow and green, which indicate a higher viewers, mostly appear at the right side of the plot, where the sentiment scores are high.

### 4) Linear model building

In this model, we set the arm "before 2010" from the categorical variable "year" as the reference. From the linear modelling result, it can be discovered that only the estimated coefficients for the number of speaker ("num_speaker") is not significant at 0.05 significance level due to the large p-value. Therefore, we can conclude that there is no significant linear association between the outcome (number of views) and the number of speakers, adjusted for other covariates in the model. Then we drop the *num_speaker* variable and refit the model.

```{r}
ted.lm = select(rat_sent, no, duration, languages, num_speaker, year, views, sentiment) %>%
  mutate(year = as.numeric(year),
         year = ifelse(year < 2010, "before 2010", 
                       ifelse(year >= 2010 & year < 2015, "between 2010 and 2015", "after 2015")),
         year = factor(year, levels = c("before 2010","between 2010 and 2015","after 2015")))

### fit model1
model1 = lm(views ~ sentiment + year + duration + languages + num_speaker, data = ted.lm)

### update model
update(model1, .~. -num_speaker) %>%
  summary() %>% 
  broom::tidy() %>% 
  pander::pander()
```

From the table above, the final model we conclude for the study is \[Views = -1.13*10^6 + 625.1 * Sentiment + 5.62*10^4 * I\{Year \ between \ 2010 \ and \ 2015\}\\
+ 4.76*10^5 * I\{Year \ after \ 2015\}  + 369.4 * Duration + 5.83*10^4 * Languages\]

As for the variable *year*, the arm "after 2015" presents significant postive estimate, indicating the positive mean difference of number of views for TED talks published after 2015 compared with the number of views for those published before 2010. In other words, TED talks published after 2015 are more popular than those published before 2010. At the same time, it can be noticed that language and duration are also strongly associated with the number of views. Specifically, in terms of "languages", the mean number of views will increase by 58350 as the number of languages in which the talk is available increases by 1 adjusted for other covariates. As expected, sentiment plays an important role in the model, implying that it is exactly reflection of popularity for TED talks to some extent. Basically, the adjusted R-square is around 60%, suggesting 60% variation in the number of views can be explained by the variation in those covariates. This values is good enough to conlcude that points representing the outcome (number of views) and predictors are well fitted on the linear model. 

## Conclusion
In this study, the question of why a TED talk becomes popular is explained by analyzing the association between the popularity, represented by the number of views, and other variables provided in the dataset. According to the results, the topic, speaker, duration of a TED talk and the number of language available are all concretely connected with the popularity of that talk. Serveral topics like technology, business and culture are prone to more popularity. The speakers and their occupations also play important roles in drawing attention of population, among which psychologists, writers, scientists and entrepreneur are most popular speaker occupations. It is also revealed that the language available for a TED talk is of importance in its popularity. Therefore, it can be suggested to have more languages available for a talk in order to improve its popularity. At last,  popularity for TED talks through time are compared, which reveals the truth that increasing poeple are joining in this sharing talks of thoughts of mind so far and the "ideas worth spreading" are truly propagating.

## Related links

```{r include=FALSE}
library("htmltools")
library("vembedr")
```

You may interested in the 5 most popular TED talks:

* **`r ted.data$name[1]`**

```{r}
embed_url("https://youtu.be/KoeFETjmUP4")
``` 

* [`r ted.data$name[1347]`](`r ted.data$url[1347]`)
* [`r ted.data$name[678]`](`r ted.data$url[678]`)
* [`r ted.data$name[838]`](`r ted.data$url[838]`)
* [`r ted.data$name[453]`](`r ted.data$url[453]`)

**For more details, you can access to our original report [here](Final_Project.html)**.